Molecular transport in human pial perivasculature

### 2024-11-27 paper/supplementary_main.tex
Minor corrections in notation in Section A.3
Former-commit-id: 1f75dc2b2672d3ba1bfe2bde2a096988001a3724

\subsubsection{Modelling CSF flow via the incompressible Stokes equations}
\label{sec:csf_flow}
The time-independent, incompressible Stokes equations model the flow
of an incompressible Newtonian fluid at low Reynolds numbers, and read
as follows: over the domain $\Omega_{\rm CSF} \subset \R^3$, find the
velocity vector field $\bm u : \Omega_{\rm CSF} \rightarrow \R^3$ and
the pressure field $p : \Omega_{\rm CSF} \rightarrow \R$ such that
\begin{subequations}
  \begin{alignat}{2}
    - \mu \Delta \bm u  + \nabla p &=  0 \quad && \text{ in } \Omega_{\rm CSF},
    \label{eq:momnetum_equation} \\ 
    \nabla \cdot \bm u &= 0 \quad && \text{ in } \Omega_{\rm CSF},
    \label{eq:divergence_equation} .
  \end{alignat}
  \label{eq:stokes}
\end{subequations}
In addition, we impose the following boundary conditions to model flow
induced by CSF production in the choroid plexus with $\Gamma_{\rm AM-U}$ as the main efflux site:
\begin{subequations}
  \begin{alignat}{2}
    \mu \nabla \bm u \cdot \bm{n} - p \bm n &= -R_0 ( \bm u \cdot \bm n ) \bm n
    && \text{ on } \Gamma_{\mathrm{AM-U}}, \\
    \bm u &= 0 && \text{ on } \Gamma_{\mathrm{AM-L}}\cup\Gamma_{\rm{pia}}\cup\Gamma_{\rm{SSAS}}, \\
    %\bm u &= 0 && \text{ on } \Gamma_{\rm{pia}}, \\
    %\bm u &= 0 && \text{ on } \Gamma_{\rm{SSAS}}, \\
    \bm u \cdot \bm n & = \frac{1}{ |\Gamma_{\rm LV}|}  u_{\rm in}, \quad \bm u \cdot \bm \tau = 0 \quad && \text{ on } \Gamma_{\rm{LV}} ,  
  \end{alignat}
  \label{eq:stokes_bcs}
\end{subequations}
where $\bm n$ denotes the unit outward normal to the boundary, $\mu$ is the (dynamic) CSF viscosity, $R_0 > 0$ is a resistance parameter for CSF efflux, and $u_{\rm in}$ is a given fluid influx, here across the lateral ventricle wall $\Gamma_{\rm LV}$. We consider alternative variations of these boundary conditions in connection with estimating dispersion effects induced by CSF pulsatility, see~\Cref{sec:supp:dispersion}.

@@

We consider a mesh $\mathcal{T} = \{ E \}$ of $\Omega = \Omega_{\rm
  PAR} \cup \Omega_{\rm CSF}$, consisting of tetrahedral mesh cells
$E$, and conforming to the domains $\Omega_{\rm PAR}$ and $\Omega_{\rm
  CSF}$ and to the CSF-brain interface $\Gamma_{\rm pia} \cup
\Gamma_{\rm LV}$. We denote the restriction of $\mathcal{T}$ to
$\Omega_{\rm PAR}$ and $\Omega_{\rm CSF}$ by $\mathcal{T}_{\rm PAR}$
and $\mathcal{T}_{\rm CSF}$, respectively. The collection of all
interior facets (faces of the mesh cells) in $\mathcal{T}_{\rm PAR}$
(resp. in $\mathcal{T}_{\rm CSF}$) is denoted by $\mathcal{F}_{i, \rm
  PAR}$ (resp. $\mathcal{F}_{i, \rm CSF}$). We define the union of
facets interior both to $\mathcal{T}_{i, \rm PAR}$ and
$\mathcal{T}_{i, \rm CSF}$ as $\mathcal{F}_i = \mathcal{F}_{i, \rm
  PAR} \cup \mathcal{F}_{i, \rm CSF}$. Facets lying on the pial
interface $\Gamma_{\rm pia}$ are denoted by $\mathcal{F}_{\rm pia}$,
on the outer (arachnoid) boundary $\Gamma_{\rm AM}$ by
$\mathcal{F}_{\rm AM}$, on the inner ventricular interface
$\Gamma_{\rm LV}$ by $\mathcal{F}_{\rm LV}$, on the boundary toward
the spinal cord $\Gamma_{\rm SC}$ by $\mathcal{F}_{\rm SC}$ and on the
boundary towards the spinal SAS $\Gamma_{\rm SSAS}$ by
$\mathcal{F}_{\rm SSAS}$. \discuss{For convenience, we denote $\mathcal{F}_e =
\mathcal{F}_{\rm pia} \cup \mathcal{F}_{\rm LV} \cup \mathcal{F}_{\rm
  AM-U} \cup \mathcal{F}_{\rm SSAS}$, and the union of all facets in
$\mathcal{T}$ is denoted by $\mathcal{F} = \mathcal{F}_i \cup
\mathcal{F}_e \discuss{\cup \mathcal{F}_{\rm SC} \cup \mathcal{F}_{\rm AM-L}}$.}

@@

We first consider the discretization of~\eqref{eq:3d_pde} and
introduce the discrete space
\begin{equation}
  %V_h^k = \{c_h \in L^2(\Omega): \;  v_h \vert_E \in \mathbb{P}^k(E), \; E \in \mathcal{T}_h\}.
  V_h^k = \{c \in L^2(\discuss{\mathcal{T}}): \;  c \vert_E \in \mathbb{P}^k(E), \; E \in \mathcal{T}\} ,
\end{equation}
where $L^2(\mathcal{T})$ is the space of square-integrable functions
defined relative to $\mathcal{T}$ and $\mathbb{P}^k(E)$ denotes the
space of polynomials of degree $\leqslant k$ defined over the
tetrahedra $E$. To discretize the diffusion term in~\eqref{eq:3d_pde},
we use a symmetric weighted interior penalty DG formulation, referring
to~\cite{ern2009discontinuous} and \cite[Section
  4.5.2.3]{di2011mathematical} for details on this
method. \discuss{Recall that $\phi$ is constant in each domain
  $\Omega_{\rm PAR}$ and $\Omega_{\rm CSF}$, and thus in particular
  that $\nabla (\phi c) = \phi \nabla c$ on each $E \in \mathcal{T}$.}
Define for $c, v \in V_h^k$:
\begin{equation}
  a_h (c, v)
  =
  \sum_{E \in \mathcal{T}} \int_{E} D \discuss{\phi} \nabla c \cdot \nabla v
  + \sum_{F \in \mathcal{F}_i} \eta \frac{\gamma_{D,F}}{h_F} \int_{F} [c][v] 
  - \sum_{F \in \mathcal{F}_i} \int_{F} \left( \{D \phi \nabla c \}_w \cdot \bm n_F [v]
  + \{D \phi \nabla v \}_w \cdot \bm n_F [c] \right).
  \label{eq:dg_sip}
\end{equation}
In~\eqref{eq:dg_sip}, for each facet $F \in \mathcal{F}^i$ shared
between cells $E^1$ and $E^2$ with facet normal vector $\bm n_F$
pointing from $E^1$ to $E^2$, \discuss{$h_F$ denotes the facet diameter},
the jump $[\cdot]$ is given by $[v] = v|_{E^1} - v|_{E^2}$, and the
unweighted average $\{ \cdot \}$ and weighed average $\{ \cdot \}_w$
are defined as:
\begin{equation}
  \{v\} = \frac12 v |_{E^1} + \frac12 v |_{E^2}, \qquad
  \{v\}_{w} = \frac{\kappa_2}{\kappa_1 + \kappa_2} v |_{E^1} + \frac{\kappa_1}{\kappa_1 + \kappa_2} v |_{E^2}
  \quad \text{where} \quad \kappa_i = \phi D|_{E^i}.  
\end{equation}
The parameter $\gamma_{D,F}$ is the harmonic mean of the
\discuss{porosity-weighted} diffusion coefficient given by
\begin{equation}
  \gamma_{D,F} = \frac{\kappa_1\kappa_2}{\kappa_1 + \kappa_2},
\end{equation}
and $\eta$ is a user-specified penalty parameter. To discretize the convection term in~\eqref{eq:3d_pde}, we use
upwinding, see \cite[Section 2.3.1]{di2011mathematical} and the
references therein. For $c, v \in V_h^k$, define
\begin{equation}
  a_h^{\mathrm{up}}(c, v)
  = - \sum_{E \in \mathcal{T}} \int_E \bm{u} c \nabla v
  + \sum_{F \in \mathcal{F}_i } \int_F \{ \bm u  c\} \cdot \bm{n}_F [v] +
  \sum_{F \in \mathcal{F}_i} \int_F \frac{|\bm u \cdot \bm n_F|}{2} [c] [v] .
\end{equation}
Our discrete formulation for \eqref{eq:3d_pde} with the interface conditions~\eqref{eq:3d_interface} and boundary conditions~\eqref{eq:3d_bcs} and given initial conditions $c_h^0$ then reads: for $n = 1, 2, \dots$, with $t^n - t^{n-1} = \tau$, find $c_h^n \in V_h^k$ such that for all $v \in V_h^k$:
\begin{equation}
  \int_{\Omega} \frac{1}{\tau} (\phi c_h^n - \phi c_h^{n-1}) v
  + a_h(c_h^n, v) + a_h^{\mathrm{up}}(c_h^n,v)
  + \int_{\Gamma_{\rm pia} \discuss{\cup \Gamma_{\rm LV}} } \beta_{\rm pia}[c_h^n][v] 
  + \int_{\Gamma_{\rm AM-U}} \beta_{\rm exit} c_h^n v 
  + \int_{\Lambda} \xi  P \left (\overline{c_h^n} - \hat c_h^n \right) \overline{v} 
  = 
  %\int_{\Omega} f^n v +
  \int_{\Gamma_{\rm \discuss{S}SAS}} g_{\rm influx} v
  %, \quad \forall v \in V_h^k
  .
\end{equation}

@@

We consider an H(div)-based finite element approximation of the incompressible Stokes equations~\eqref{eq:stokes} defined over $\Omega_{\rm CSF}$ with the boundary conditions~\eqref{eq:stokes_bcs}. Following\cite{hong2016robust}, we approximate the velocity field $\bm u$ and the pressure field $p$ with the following finite element spaces:
\begin{align*}
  \bm V_h &= \{ \bm v  \in H(\mathrm{div}, \Omega_{\mathrm{CSF}}): \;
  \bm v \vert_{E} \in \mathrm{BDM}^2(E), \; E \in \mathcal{T}_{\rm CSF}; \;
  \bm v \cdot \bm n = 0
  \text{ on } \Gamma_{\rm{pia}} \cup \Gamma_{\rm AM-L} \cup \Gamma_{\rm{SSAS}}, \;\; \bm v \cdot \bm n = \frac{1}{|\Gamma_{\mathrm{LV}}|} u_{\mathrm{in}} \text{ on } \Gamma_{\mathrm{LV}} \}  \\ 
  Q_h  &= \{q \in L^2(\Omega_{\rm CSF}): \; q \vert_E \in \mathbb{P}^1(E),
  \; E \in \mathcal{T}_{\rm CSF} \}. 
\end{align*}
Here, $H(\mathrm{div}, \Omega)$ is the space of $L^2(\Omega)$ vector fields with $L^2(\Omega)$ divergence, $\mathrm{BDM}^2$ is the Brezzi-Douglas--Marini element~\cite{brezzi1987mixed} of degree 2, and $\bm n$ and $\bm \tau$ are the unit outward normal and unit tangent vectors to each facet, respectively. Given any vector $\bm v$, the normal and tangential components on each facet are denoted and given by 
\begin{equation}
\bm v_n = (\bm v \cdot \bm n) \bm n, \quad \bm v_t = \bm v - \bm v_n. 
\end{equation}
Since $\bm V_h \subset H(\mathrm{div}, \Omega_{\rm CSF})$, then $[\bm v_n] = 0 $ on $\mathcal{F}_{\rm CSF}$. Continuity in the tangential component is enforced weakly via interior penalization. Define the form \mer{MER: Check $\Gamma_{\rm AM}$ part. 26.11.24: Rami will check $\mathcal{F}_e$ versus definitions of the boundaries and where it appears.}
\begin{multline}
  \mathcal{A}_h(\bm u, \bm v)
  = \sum_{E \in \mathcal{T}_{\rm CSF}} \int_{E} \mu \nabla \bm u : \nabla \bm v
  - \sum_{F \in \discuss{\mathcal{F}_{\rm CSF} \cup \mathcal{F}_{e}}} \left (
  \int_{F} \mu \{\nabla \bm u\} \cdot \bm n_F \cdot [\bm v_t] 
  - %\sum_{F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma}}
  \int_{F} \mu \{\nabla \bm v\}\cdot \bm n_F \cdot [\bm u_t]
  + %\sum_{F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma}}
  \frac{\sigma \mu}{h} \int_{F} [\bm u_t ] \cdot [\bm v_t] \right ),   
\end{multline}
where \discuss{$h$ denotes the element size}. We set the penalty parameter for the tangential continuity to be $\sigma = 20$. Our finite element discretization of the incompressible Stokes equations is then to find $(\bm u_h, p_h) \in \bm V_h \times Q_h$ such that 
\begin{subequations}
\begin{align}
  \mathcal{A}_h(\bm u_h, \bm v_h)
  + \sum_{F \in \mathcal{F}_{\rm AM-U}} \int_{F} R_0 (\bm u_h \cdot \bm n) (\bm v_h \cdot \bm n)
  - \int_{\Omega_{\rm CSF}} \nabla \cdot \bm v_h \, p_h  &= 0, \qquad \foralls \bm v_h \in \bm V_h, \\ 
\int_{\Omega_{\rm CSF}} \nabla \cdot \bm u_h \, q_h  &= 0, \qquad \foralls q_h \in Q_h.
\end{align}
\end{subequations}

>>>>

\subsubsection{Modelling CSF flow via the incompressible Stokes equations}
\label{sec:csf_flow}
The time-independent, incompressible Stokes equations model the flow
of an incompressible Newtonian fluid at low Reynolds numbers, and read
as follows: over the domain $\Omega_{\rm CSF} \subset \R^3$, find the
velocity vector field $\bm u : \Omega_{\rm CSF} \rightarrow \R^3$ and
the pressure field $p : \Omega_{\rm CSF} \rightarrow \R$ such that
\begin{subequations}
  \begin{alignat}{2}
    - \mu \Delta \bm u  + \nabla p &=  0 \quad && \text{ in } \Omega_{\rm CSF},
    \label{eq:momnetum_equation} \\ 
    \nabla \cdot \bm u &= 0 \quad && \text{ in } \Omega_{\rm CSF},
    \label{eq:divergence_equation} .
  \end{alignat}
  \label{eq:stokes}%
\end{subequations}%
In addition, we impose the following boundary conditions to model flow
induced by CSF production in the choroid plexus with $\Gamma_{\rm AM-U}$ as the main efflux site:
\begin{subequations}
  \begin{alignat}{2}
    \mu \nabla \bm u \cdot \bm{n} - p \bm n &= -R_0 ( \bm u \cdot \bm n ) \bm n
    && \text{ on } \Gamma_{\mathrm{AM-U}}, \\
    \bm u &= 0 && \text{ on } \Gamma_{\mathrm{AM-L}}\cup\Gamma_{\rm{pia}}\cup\Gamma_{\rm{SSAS}}, \\
    %\bm u &= 0 && \text{ on } \Gamma_{\rm{pia}}, \\
    %\bm u &= 0 && \text{ on } \Gamma_{\rm{SSAS}}, \\
    \bm u \cdot \bm n & = \frac{1}{ |\Gamma_{\rm LV}|}  u_{\rm in}, \quad \bm u \cdot \bm \tau = 0 \quad && \text{ on } \Gamma_{\rm{LV}} ,  
  \end{alignat}
  \label{eq:stokes_bcs}%
\end{subequations}%
where $\bm n$ denotes the unit outward normal to the boundary, $\mu$ is the (dynamic) CSF viscosity, $R_0 > 0$ is a resistance parameter for CSF efflux, and $u_{\rm in}$ is a given fluid influx, here across the lateral ventricle wall $\Gamma_{\rm LV}$. We consider alternative variations of these boundary conditions in connection with estimating dispersion effects induced by CSF pulsatility, see~\Cref{sec:supp:dispersion}.

@@

We consider a mesh $\mathcal{T} = \{ E \}$ of $\Omega = \Omega_{\rm
  PAR} \cup \Omega_{\rm CSF}$, consisting of tetrahedral mesh cells
$E$, and conforming to the domains $\Omega_{\rm PAR}$ and $\Omega_{\rm
  CSF}$ and to the CSF-brain interface $\Gamma_{\rm pia} \cup
\Gamma_{\rm LV}$. We denote the restriction of $\mathcal{T}$ to
$\Omega_{\rm PAR}$ and $\Omega_{\rm CSF}$ by $\mathcal{T}_{\rm PAR}$
and $\mathcal{T}_{\rm CSF}$, respectively. The collection of all
interior facets (i.e.~triangular faces of the tetrahedral mesh cells)
in $\mathcal{T}_{\rm PAR}$ and $\mathcal{T}_{\rm CSF}$ are denoted by
$\mathcal{F}_{i, \rm PAR}$ and $\mathcal{F}_{i, \rm CSF}$,
respectively. We define the union of facets interior both to
$\mathcal{T}_{i, \rm PAR}$ and $\mathcal{T}_{i, \rm CSF}$ as
$\mathcal{F}_i = \mathcal{F}_{i, \rm PAR} \cup \mathcal{F}_{i, \rm
  CSF}$. Facets lying on the pial interface $\Gamma_{\rm pia}$ are
denoted by $\mathcal{F}_{\rm pia}$, on the outer (arachnoid) boundary
$\Gamma_{\rm AM}$ by $\mathcal{F}_{\rm AM}$, on the inner ventricular
interface $\Gamma_{\rm LV}$ by $\mathcal{F}_{\rm LV}$, on the boundary
toward the spinal cord $\Gamma_{\rm SC}$ by $\mathcal{F}_{\rm SC}$ and
on the boundary towards the spinal SAS $\Gamma_{\rm SSAS}$ by
$\mathcal{F}_{\rm SSAS}$. \discuss{For convenience, we denote
  $\mathcal{F}_e = \mathcal{F}_{\rm pia} \cup \mathcal{F}_{\rm LV}
  \cup \mathcal{F}_{\rm AM-U} \cup \mathcal{F}_{\rm SSAS}$, and the
  union of all facets in $\mathcal{T}$ is denoted by $\mathcal{F} =
  \mathcal{F}_i \cup \mathcal{F}_e \discuss{\cup \mathcal{F}_{\rm SC}
    \cup \mathcal{F}_{\rm AM-L}}$.}

@@

We first consider the discretization of~\eqref{eq:3d_pde} and
introduce the discrete space
\begin{equation}
  %V_h^k = \{c_h \in L^2(\Omega): \;  v_h \vert_E \in \mathbb{P}^k(E), \; E \in \mathcal{T}_h\}.
  V_h^k = \{c \in L^2(\Omega): \;  c \vert_E \in \mathbb{P}^k(E), \; E \in \mathcal{T}\} ,
\end{equation}
where $L^2(\Omega)$ is the space of square-integrable functions
defined over $\Omega$ and $\mathbb{P}^k(E)$ denotes the space of
polynomials of degree $\leqslant k$ defined over the tetrahedra
$E$. To discretize the diffusion term in~\eqref{eq:3d_pde}, we use a
symmetric weighted interior penalty DG formulation, referring
to~\cite{ern2009discontinuous} and \cite[Section
  4.5.2.3]{di2011mathematical} for details on this
method. \discuss{Recall that $\phi$ is constant in each domain
  $\Omega_{\rm PAR}$ and $\Omega_{\rm CSF}$, and thus in particular
  that $\nabla (\phi c) = \phi \nabla c$ on each $E \in \mathcal{T}$.}
Define for $c, v \in V_h^k$:
\begin{equation}
  a_h (c, v)
  =
  \sum_{E \in \mathcal{T}} \int_{E} D \discuss{\phi} \nabla c \cdot \nabla v
  + \sum_{F \in \mathcal{F}_i} \eta \frac{\gamma_{D,F}}{h_F} \int_{F} [c][v] 
  - \sum_{F \in \mathcal{F}_i} \int_{F} \left( \{D \phi \nabla c \}_w \cdot \bm n_F [v]
  + \{D \phi \nabla v \}_w \cdot \bm n_F [c] \right).
  \label{eq:dg_sip}
\end{equation}
In~\eqref{eq:dg_sip}, for each facet $F \in \mathcal{F}^i$ shared
between cells $E^1$ and $E^2$ with facet normal vector $\bm n_F$
pointing from $E^1$ to $E^2$, \discuss{$h_F$ denotes the facet diameter},
the jump $[\cdot]$ is given by $[v] = v|_{E^1} - v|_{E^2}$, and the
unweighted average $\{ \cdot \}$ and weighed average $\{ \cdot \}_w$
are defined as:
\begin{equation}
  \{v\} = \frac12 v |_{E^1} + \frac12 v |_{E^2}, \qquad
  \{v\}_{w} = \frac{\kappa_2}{\kappa_1 + \kappa_2} v |_{E^1} + \frac{\kappa_1}{\kappa_1 + \kappa_2} v |_{E^2}
  \quad \text{where} \quad \kappa_i = \phi D|_{E^i}.  
\end{equation}
The parameter $\gamma_{D,F}$ is the harmonic mean of the
\discuss{porosity-weighted} diffusion coefficient given by
\begin{equation}
  \gamma_{D,F} = \frac{\kappa_1\kappa_2}{\kappa_1 + \kappa_2},
\end{equation}
and $\eta$ is a user-specified penalty parameter. To discretize the convection term in~\eqref{eq:3d_pde}, we use
upwinding, see \cite[Section 2.3.1]{di2011mathematical} and the
references therein. For $c, v \in V_h^k$, define
\begin{equation}
  a_h^{\mathrm{up}}(c, v)
  = - \sum_{E \in \mathcal{T}} \int_E \bm{u} c \nabla v
  + \sum_{F \in \mathcal{F}_i } \int_F \{ \bm u  c\} \cdot \bm{n}_F [v] +
  \sum_{F \in \mathcal{F}_i} \int_F \frac{|\bm u \cdot \bm n_F|}{2} [c] [v] .
\end{equation}
Our discrete formulation for \eqref{eq:3d_pde} with the interface conditions~\eqref{eq:3d_interface} and boundary conditions~\eqref{eq:3d_bcs} and given initial conditions $c_h^0$ then reads: for $n = 1, 2, \dots$, with $t^n - t^{n-1} = \tau$, find $c_h^n \in V_h^k$ such that for all $v \in V_h^k$:
\begin{equation}
  \int_{\Omega} \frac{1}{\tau} (\phi c_h^n - \phi c_h^{n-1}) v
  + a_h(c_h^n, v) + a_h^{\mathrm{up}}(c_h^n,v)
  + \int_{\Gamma_{\rm pia} \discuss{\cup \Gamma_{\rm LV}} } \beta_{\rm pia}[c_h^n][v] 
  + \int_{\Gamma_{\rm AM-U}} \beta_{\rm exit} c_h^n v 
  + \int_{\Lambda} \xi  P \left (\overline{c_h^n} - \hat c_h^n \right) \overline{v} 
  = 
  %\int_{\Omega} f^n v +
  \int_{\Gamma_{\rm \discuss{S}SAS}} g_{\rm influx} v
  %, \quad \forall v \in V_h^k
  .
\end{equation}

@@

We consider an H(div)-based finite element approximation of the incompressible Stokes equations~\eqref{eq:stokes} defined over $\Omega_{\rm CSF}$ with the boundary conditions~\eqref{eq:stokes_bcs}. Following\cite{hong2016robust}, we approximate the velocity field $\bm u$ and the pressure field $p$ with the following finite element spaces:
\begin{align*}
  \bm V_h &= \{ \bm v  \in H(\mathrm{div}, \Omega_{\mathrm{CSF}}): \;
  \bm v \vert_{E} \in \mathrm{BDM}^2(E), \; E \in \mathcal{T}_{\rm CSF}; \;
  \bm v \cdot \bm n = 0
  \text{ on } \Gamma_{\rm{pia}} \cup \Gamma_{\rm AM-L} \cup \Gamma_{\rm{SSAS}}, \;\; \bm v \cdot \bm n = \frac{1}{|\Gamma_{\mathrm{LV}}|} u_{\mathrm{in}} \text{ on } \Gamma_{\mathrm{LV}} \}  \\ 
  Q_h  &= \{q \in L^2(\Omega_{\rm CSF}): \; q \vert_E \in \mathbb{P}^1(E),
  \; E \in \mathcal{T}_{\rm CSF} \}. 
\end{align*}
Here, $H(\mathrm{div}, \Omega)$ is the space of $L^2(\Omega)$ vector fields with $L^2(\Omega)$ divergence, $\mathrm{BDM}^2$ is the Brezzi-Douglas--Marini element~\cite{brezzi1987mixed} of degree 2, and $\bm n$ and $\bm \tau$ are the unit outward normal and unit tangent vectors to each facet, respectively. Given any vector $\bm v$, the normal and tangential components on each facet are denoted and given by 
\begin{equation}
\bm v_n = (\bm v \cdot \bm n) \bm n, \quad \bm v_t = \bm v - \bm v_n. 
\end{equation}
Since $\bm V_h \subset H(\mathrm{div}, \Omega_{\rm CSF})$, then $[\bm v_n] = 0 $ on $\mathcal{F}_{i, \rm CSF}$. Continuity in the tangential component is enforced weakly via interior penalization. Define the form \mer{MER: Check $\Gamma_{\rm AM}$ part. 26.11.24: Rami will check $\mathcal{F}_e$ versus definitions of the boundaries and where it appears.}
\begin{multline}
  \mathcal{A}_h(\bm u, \bm v)
  = \sum_{E \in \mathcal{T}_{\rm CSF}} \int_{E} \mu \nabla \bm u : \nabla \bm v
  - \sum_{F \in \discuss{\mathcal{F}_{i, \rm CSF} \cup \mathcal{F}_{e}}} \left (
  \int_{F} \mu \{\nabla \bm u\} \cdot \bm n_F \cdot [\bm v_t] 
  - %\sum_{F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma}}
  \int_{F} \mu \{\nabla \bm v\}\cdot \bm n_F \cdot [\bm u_t]
  + %\sum_{F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma}}
  \frac{\sigma \mu}{h} \int_{F} [\bm u_t ] \cdot [\bm v_t] \right ),   
\end{multline}
where \discuss{$h$ denotes the element size}. We set the penalty parameter for the tangential continuity to be $\sigma = 20$. Our finite element discretization of the incompressible Stokes equations is then to find $(\bm u_h, p_h) \in \bm V_h \times Q_h$ such that 
\begin{subequations}
\begin{align}
  \mathcal{A}_h(\bm u_h, \bm v_h)
  + \sum_{F \in \mathcal{F}_{\rm AM-U}} \int_{F} R_0 (\bm u_h \cdot \bm n) (\bm v_h \cdot \bm n)
  - \int_{\Omega_{\rm CSF}} \nabla \cdot \bm v_h \, p_h  &= 0, \qquad \foralls \bm v_h \in \bm V_h, \\ 
\int_{\Omega_{\rm CSF}} \nabla \cdot \bm u_h \, q_h  &= 0, \qquad \foralls q_h \in Q_h.
\end{align}
\end{subequations}
